---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MKHthemes

<!-- badges: start -->
[![R-CMD-check](https://github.com/MatthewHeun/MKHthemes/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/MatthewHeun/MKHthemes/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

## Statement of need

The default appearance of `ggplot2` graphics is unattractive. 
Tick marks point outward (away from the data).
Grid lines are provided (are we in jail?).
Borders are black (taking focus away from the data).

This package (`MKHthemes`) provides 
a nice-looking theme for `ggplot2` graphs.


## Installation

You can install `MKHthemes` from GitHub with:

```{r gh-installation, eval = FALSE}
# install devtools if not already installed
# install.packages("devtools")
devtools::install_github("MatthewHeun/MKHthemes")
# To build vignettes locally, use
devtools::install_github("MatthewHeun/MKHthemes", build_vignettes = TRUE)
```


## More Information

Find more information, including vignettes and function documentation, at 
<https://MatthewHeun.github.io/MKHthemes/>.
