---
title: "MKHthemes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MKHthemes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  fig.retina = 2, 
  fig.width = 6, 
  fig.height = 4, 
  fig.align = "center"
)
```

```{r setup, echo=FALSE}
library(ggplot2)
library(MKHthemes)
library(tibble)
```

## Introduction

[ggplot2](https://ggplot2.tidyverse.org) is awesome! 
However, some of its defaults are ... undesirable and ugly.
`MKHthemes` provides ways to improve [ggplot2](https://ggplot2.tidyverse.org) graphs.
By default, `MKHthemes` provides more pleasing graphs 
than [ggplot2](https://ggplot2.tidyverse.org), and
it includes a few options to tweak graphs easily.

The package contains only one function, `xy_theme()`.
By default, `xy_theme()` looks great.
Arguments provide easy ways to adjust commonly needed but esoteric settings
that are hidden deep within [ggplot2](https://ggplot2.tidyverse.org).
This vignette describes the function `xy_theme()`
and its arguments.


## Sample data

Here is a data frame for the examples that follow.
It contains descenders for facet labels, 
to ensure the labels are positioned correctly.

```{r}
df <- tibble::tribble(~x, ~y, ~EorX,     ~Country, 
                       1,  2, "Energy",  "Georgia", 
                       2,  3, "Energy",  "Georgia",
                       4,  5, "Exergy",  "Georgia",
                       6,  7, "Exergy",  "Georgia",
                      11, 12, "Energy",  "Fiji", 
                      12, 13, "Energy",  "Fiji",
                      14, 15, "Exergy",  "Fiji",
                      16, 17, "Exergy",  "Fiji")
df
```

## A first example

The default settings for [ggplot2](https://ggplot2.tidyverse.org)
give the following graph.

```{r}
p <- df |> 
  ggplot2::ggplot(mapping = ggplot2::aes(x = x, y = y, colour = Country)) + 
  ggplot2::geom_line() + 
  ggplot2::facet_grid(rows = ggplot2::vars(Country), 
                      cols = ggplot2::vars(EorX))
p
```

I find the figure quite ugly:

* Gray background? Really? 
  Graphs should be made with the least amount of ink. 
  (See [Edward Tufte](https://www.edwardtufte.com/).)
  Too much ink spilt for the background.
* Dark gray background for the facet labels? 
  Again, too much ink is allocated to non-data elements.
* Tick marks outside of the plot?
  All elements of a graph should point toward the data, not away from it.
  Tick marks outside point away from the data.
  Tick marks inside point toward the data and are preferred.
* Grid lines?
  They put the viewer in jail.
  
To improve the appearance of the graph, 
use `xy_theme()`.

```{r}
p + MKHthemes::xy_theme()
```

By default, `xy_theme()`

* eliminates the background colour to reduce the amount of ink in the plot,
* adds inward-pointing tick marks to point toward the data,
* provides a thin gray border around the graphs to frame the data,
* sets gray text for the border elements to push them to the visual background, and
* enables easy fine-tuning of many esoteric settings
  in the unlikely event that you disagree with any of the above.


## Adjustments

`xy_theme()` provides several arguments 
that enable easy adjustments of graphical parameters, 
as shown in the following examples.

```{r}
# Change font size. Default is 12 points.
p + MKHthemes::xy_theme(font_size = 8)
# Change font family. Default is "", a sans-serif font.
p + MKHthemes::xy_theme(font_family = "Times New Roman")
# Change size of all non-axis-title fonts.
p + MKHthemes::xy_theme(font_size_scale = 0.4)
# Adjust tick length in points. Default is -0.3*font_size.
# Negative values are strongly recommended, 
# because they point the ticks inward.
p + MKHthemes::xy_theme(tick_length = -7)
# Adjust spacing between axis values and the border in points. 
# Defaults are 0.2*font_size.
p + MKHthemes::xy_theme(x_axis_labels_spacing = -5,
                        y_axis_labels_spacing = 20)
# Change facet label distance from the graph in points. 
# Defaults are 0.2*font_size.
p + MKHthemes::xy_theme(col_facet_labels_spacing = -3,
                        row_facet_labels_spacing = 20)
# Change border and label colour. Default is "gray50".
p + MKHthemes::xy_theme(border_and_label_colour = "red")
```


## `MKHthemes` and `microtype`

Note that `xy_theme()` scales fonts to arbitrary precision.
If you use `MKHthemes` with [knitr](https://yihui.org/knitr/) 
within [$\LaTeX$](https://www.latex-project.org), 
you may need to disable font scaling by the `microtype` package
to avoid errors on Windows machines. 
We have found the following code helpful.

```
\usepackage{microtype}
\microtypesetup{expansion=false}
```

  
## Conclusion
  
`MKHthemes` provides pleasing [ggplot2](https://ggplot2.tidyverse.org) graphics, 
with sensible defaults and easy adjustment
to otherwise-esoteric [ggplot2](https://ggplot2.tidyverse.org) settings.
  
