---
title: "MKHthemes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MKHthemes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  fig.retina = 2, 
  fig.width = 6, 
  fig.height = 4, 
  fig.align = "center"
)
```

```{r setup}
library(ggplot2)
library(MKHthemes)
library(tibble)
```

## Introduction

`ggplot2` is awesome! 
However, some of its features are ... less than desirable.
This package provides ways to improve on its presentation of graphs.
By default, it provides a more pleasant version of graphs than `ggplot2`, and
it includes a few options to tweak graphs easily.

The package contains only one function, `MKHthemes::xy_theme()`.
By default, `MKHthemes::xy_theme()` gives aesthetically pleasing graphs.
Arguments to the function provide easy ways to adjust commonly needed settings
that are esoteric and hidden deeply within `ggplot2`.
The following sections describe the function `MKHthemes::xy_theme()`
and its arguments.


## Sample data

Here is a data frame of data we can use for the examples that follow.

```{r}
df <- tibble::tribble(~x, ~y, ~EorX,     ~Country, 
                       1,  2, "Energy",  "Georgia", 
                       2,  3, "Energy",  "Georgia",
                       4,  5, "Exergy",  "Georgia",
                       6,  7, "Exergy",  "Georgia",
                      11, 12, "Energy",  "Fiji", 
                      12, 13, "Energy",  "Fiji",
                      14, 15, "Exergy",  "Fiji",
                      16, 17, "Exergy",  "Fiji")
df
```

## A first example

The default settings for `ggplot2` give the following graph.

```{r}
p <- df |> 
  ggplot2::ggplot(mapping = ggplot2::aes(x = x, y = y)) + 
  ggplot2::geom_line() + 
  ggplot2::facet_grid(rows = ggplot2::vars(Country), 
                      cols = ggplot2::vars(EorX))
p
```

I find the figure above to be quite ugly:

* Gray background? Really? 
  Edward Tufte says that graphs should be made with the least amount of ink. 
  Too much ink spilled on the background.
* Dark gray background for the facet labels? 
  Again, too much ink spilled for non-data elements.
* Tick marks outside of the plot. 
  All elements of a graph should point toward the data, not away from it.
  Tick marks outside point away from the data.
  Tick marks inside point toward the data.
* Grid lines?  
  They make the view feel like they're incarcerated.  
  
To improve the appearance of the graph, 
use `MKHthemes::xy_theme()`.

```{r}
p + MKHthemes::xy_theme()
```

`MKHthemes::xy_theme()`

* eliminates the background colour,
* adds inward-pointing tick marks,
* provides a gray border around the graphs,
* sets gray text for the graphics, and
* enables easy fine-tuning of many esoteric settings.

Each of these changes to the default theme both
foregrounds the data and
backgrounds the non-data elements of the graph.


## Adjustments

`MKHthemes::xy_theme()` provides several arguments 
that enable easy adjustments of graphical parameters, 
as shown in the following examples.

```{r}
# Change font size. Default is 12 points.
p + MKHthemes::xy_theme(font_size = 8)
# Change font family. Default is "", a sans-serif font.
p + MKHthemes::xy_theme(font_family = "Times New Roman")
# Adjust tick length in points. Default is -0.3*font_size.
# Negative values are strongly recommended, 
# because they point the ticks inward.
p + MKHthemes::xy_theme(tick_length = -7)
# Adjust spacing between axis values and the border in points. Defaults are 0.2*font_size.
p + MKHthemes::xy_theme(x_axis_labels_spacing = 0, y_axis_labels_spacing = 20)
# Change facet label distance from the graph in points. Defaults are 0.2*font_size.
p + MKHthemes::xy_theme(x_strip_labels_spacing = -3, y_strip_labels_spacing = 20)
# Change border and label colour. Default is "gray50".
p + MKHthemes::xy_theme(border_and_label_colour = "red")
```
  
  
## Conclusion
  
`MKHthemes` provides nice-looking `ggplot2` graphics, 
with sensible defaults and easy adjustment
to otherwise-esoteric settings.
  
